Plots

### 2025-06-25 manuscript/latex/manuscript.tex
Workaround to convert tex to docx; Convert pdf in word, then use pandoc with zotero lua to get citations for copy/paste

This study outlines the methodology used to compare cause of death (COD) assignments from four models, GPT-3.5, GPT-4, InterVA-5, and InSilicoVA, with physician-determined CODs, as summarized in Figure \ref{fig-methods-brief}. The dataset was first filtered to include only records with physician agreement, as described in Section \ref{methods-data}. Section \ref{methods-models} details the input formats and output structures of the four models. Section~\ref{methods-eval} presents the evaluation framework, which compares model outputs to physician-assigned CODs using both population-level and individual-level performance metrics. Additional methodological details are provided in Appendix \ref{app-methods}.

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-methods-brief.pdf}
\caption{Study methods.}\label{fig-methods-brief}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-pccc-csmf.pdf}
\caption{Overall model performance.}\label{fig-pccc-csmf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-pccc.pdf}
\caption{Model performance by age group.}\label{fig-pccc}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-pccc-age.pdf}
\caption{Model performance by age range.}\label{fig-pccc-age}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{fig-pccc-cod-adult.pdf}
\caption{Model performance for adult records by COD.}\label{fig-pccc-cod-adult}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-pccc-cod-child.pdf}
\caption{Model performance for child records by COD.}\label{fig-pccc-cod-child}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-pccc-cod-neo.pdf}
\caption{Model performance for neonatal records by COD.}\label{fig-pccc-cod-neo}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{fig-discuss-phyassist.pdf}
    \caption{Model suggestions integrated in the physician assignment process.}\label{fig-discuss-phyassist}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.7\textwidth]{fig-methods.pdf}
\caption{Detailed study methods.}\label{fig-methods}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.75\textwidth]{fig-map.pdf}
\caption{Study data sampling areas.}\label{fig-map}
\end{figure}

>>>>

This study outlines the methodology used to compare cause of death (COD) assignments from four models, GPT-3.5, GPT-4, InterVA-5, and InSilicoVA, with physician-determined CODs, as summarized in Figure \ref{fig-methods-brief}. The dataset was first filtered to include only records with physician agreement, as described in Section \ref{methods-data}. Section \ref{methods-models} details the input formats and output structures of the four models. Section~\ref{methods-eval} presents the evaluation framework, which compares model outputs to physician-assigned CODs using both population-level and individual-level performance metrics. Additional details are provided in Appendix \ref{app-methods}.

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-methods-brief.pdf}
\caption{Study methods.}\label{fig-methods-brief}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc-csmf.pdf}
\caption{Overall model performance.}\label{fig-pccc-csmf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc.pdf}
\caption{Model performance by age group.}\label{fig-pccc}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc-age.pdf}
\caption{Model performance by age range.}\label{fig-pccc-age}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{../figures/fig-pccc-cod-adult.pdf}
\caption{Model performance for adult records by COD.}\label{fig-pccc-cod-adult}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc-cod-child.pdf}
\caption{Model performance for child records by COD.}\label{fig-pccc-cod-child}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc-cod-neo.pdf}
\caption{Model performance for neonatal records by COD.}\label{fig-pccc-cod-neo}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{../figures/fig-discuss-phyassist.pdf}
    \caption{Model suggestions integrated in the physician assignment process.}\label{fig-discuss-phyassist}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.7\textwidth]{../figures/fig-methods.pdf}
\caption{Detailed study methods.}\label{fig-methods}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.75\textwidth]{../figures/fig-map.pdf}
\caption{Study data sampling areas.}\label{fig-map}
\end{figure}

### 2025-06-25 src/plots.Rmd
Workaround to convert tex to docx; Convert pdf in word, then use pandoc with zotero lua to get citations for copy/paste

# Save plot
ggsave(
    "../manuscript/fig-pccc-csmf.pdf",
    fig_pccc_csmf,
    width = 170,
    height = 100,
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/fig-pccc.pdf",
    fig_pccc,
    width = 170,
    height = 75,
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-adult.pdf",
    fig_pccc_cod_adult,
    width = 170, # min 170 mm full / 85 mm half
    height = 225, # max 225 mm
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-child.pdf",
    fig_pccc_cod_child,
    width = 170,
    height = 150,
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-neo.pdf",
    fig_pccc_cod_neo,
    width = 170,
    height = 100,
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/fig-pccc-age.pdf",
    fig_pccc_age,
    width = 170,
    height = 100,
    units = "mm",
    dpi = 300
)

>>>>

# Save plot
ggsave(
    "../manuscript/figures/fig-pccc-csmf.pdf",
    fig_pccc_csmf,
    width = 170,
    height = 100,
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/figures/fig-pccc.pdf",
    fig_pccc,
    width = 170,
    height = 75,
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/figures/fig-pccc-cod-adult.pdf",
    fig_pccc_cod_adult,
    width = 170, # min 170 mm full / 85 mm half
    height = 225, # max 225 mm
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/figures/fig-pccc-cod-child.pdf",
    fig_pccc_cod_child,
    width = 170,
    height = 150,
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/figures/fig-pccc-cod-neo.pdf",
    fig_pccc_cod_neo,
    width = 170,
    height = 100,
    units = "mm",
    dpi = 300
)

@@

# Save plot
ggsave(
    "../manuscript/figures/fig-pccc-age.pdf",
    fig_pccc_age,
    width = 170,
    height = 100,
    units = "mm",
    dpi = 300
)
